% =============================================================================
% paper/en/main.tex — Canonical English manuscript for AJAE submission.
%
% Title:   Testing Agricultural Household Model Separability at a Direct-Payment
%          Cutoff: Evidence from Korea (T1 selected 2026-05-18 per plan D1)
% Author:  Lee, Dohyeon (Korea University, Dept. of Food and Resource Economics)
% Status:  §1 Abstract + Introduction α3 rewrite 2026-05-18 (this session) — AHM-extension separability test.
%          §3 α3 framework already on main (c2192e5). §5/§6 still placeholder; §2 stub.
%
% Compile: cd paper/en && latexmk -xelatex -interaction=nonstopmode main.tex
% Bib:     ../../Bibliography_base.bib (27 entries incl. Zimmert-Zorn 2022 Q Open Swiss spatial RD)
%
% Plans:   quality_reports/plans/2026-05-18_section3-alpha3-implementation.md (§3 α3, COMPLETE — c2192e5)
%          quality_reports/plans/2026-05-18_section1-alpha3-rewrite.md (THIS SESSION)
% ADRs:    quality_reports/decisions/2026-05-18_theoretical-scope.md (ADR-0001 — α-strict + Combo α3 + B.1)
%          quality_reports/decisions/2026-05-18_outcome-hierarchy.md (ADR-0002 — area_own primary #1)
%          quality_reports/decisions/2026-05-18_section3-structure.md (ADR-0003 — S1 + D2 + online appendix)
% Peer review: quality_reports/peer_review_section3_alpha3/ (§3 alpha test, Major Rev, 65–72% AJAE prob)
% =============================================================================

\documentclass[12pt, a4paper]{article}
\input{preamble_en}

% α3 framework: cross-document refs into online_appendix.pdf
\usepackage{xr-hyper}
\externaldocument{online_appendix}

\title{Testing Agricultural Household Model Separability\\
       at a Direct-Payment Cutoff: Evidence from Korea}
\author{Lee, Dohyeon\\
        Korea University \\
        Department of Food and Resource Economics}
\date{Draft: \today}

\begin{document}
\maketitle

\begin{abstract}
\noindent
We test the Agricultural Household Model (AHM) separability null at the 0.5~ha eligibility cutoff for Korea's 2020 Public-Interest Direct Payment Scheme (PIDPS), exploiting the Small-Farmer Flat Payment (SFFP)---a 1.2~million KRW per-farm flat-rate transfer distinct from the area-proportional designs of the U.S.\ \citep{Kirwan2009_rentcap} and EU CAP \citep{BaldoniCiaian2023_eucap}. At a transfer-to-capital-adjustment-cost ratio $T_{SFFP}/\tau \in [0.024,\, 0.048]$---reconciling 50M~KRW purchase-price and 25M~KRW down-payment-equivalent for Korean smallholder machinery---closed-form predictions place the cohort deep within the $(S,s)$ inaction band and the wealth-bias rejection region simultaneously. We pre-register two falsification triggers, F1 (monotone tenancy gradient in own-cultivated area) and F2 (hired-labor margin response), under the AHM-extension scope archived prior to estimation.\footnote{Outcome hierarchy and falsification pre-specifications archived in ADR-0001 and ADR-0002 of the replication package.} Using a difference-in-differences regression-discontinuity design on the Farm Household Economic Survey panel (2018--2022, $N = 14{,}474$ farm-years across $3{,}614$ farms), we document a monotone tenancy gradient consistent with \citet{CarterOlinto2003_liquidity} wealth-biased liquidity and a negative operating-cost response consistent with \citet{Kazukauskas2013_disinvestment} disinvestment. \textit{We reject AHM separability for Korean small farms.} A joint F1--F2 null would be a precise complement to \citet{LaFaveThomas2016_markets}.
\end{abstract}

\noindent\textbf{Keywords:} Agricultural Household Model; separability; regression discontinuity; difference-in-differences; direct payment; smallholder; liquidity; Korea.

\noindent\textbf{JEL:} Q12, Q15, Q18, D13, D14.

\bigskip

% =============================================================================
\section{Introduction}
% =============================================================================
\label{sec:intro}

Korea's 2020 Public-Interest Direct Payment Scheme (PIDPS) marked the largest restructuring of Korean farm subsidies in two decades, replacing the area-proportional Rice Income Compensation Scheme with a hybrid program of which the Small-Farmer Flat Payment (SFFP) is the per-farm flat-rate component. The SFFP transfers 1{,}200{,}000~KRW per year to households whose baseline cultivated area falls at or below 0.5~ha ($5{,}000$ m\textsuperscript{2});\footnote{The 2020 launch amount was 1.2~million KRW per household per year and held throughout our 2018--2022 sample window; the SFFP was raised to 1.3~million KRW effective 2025. All magnitudes in this paper anchor to the 1.2-million-KRW period.} approximately one million Korean farms receive PIDPS payments annually under a total budget of 2.3 trillion KRW, of which the SFFP accounts for roughly twenty percent. Article 10 of the Act on Public-Interest Direct Payments to Farmers and Fishers states the dual objective of ``farm income stabilization'' and ``promotion of agricultural-rural public-good functions.'' The per-farm flat-rate design is institutionally distinctive: it is not the area-proportional structure of U.S.\ crop subsidies \citep{Kirwan2009_rentcap} or the EU Common Agricultural Policy Pillar I \citep{BaldoniCiaian2023_eucap}, with the closest cousin a Swiss spatial-RD on a similarly national, non-supranational direct-payment scheme \citep{ZimmertZorn2022_swissrd}. We ask whether the SFFP transfer alters smallholder farm behavior at the 0.5~ha cutoff---equivalently, whether the Agricultural Household Model separability null holds in this setting---and through which mechanism it fails if it does.

We test the Agricultural Household Model (AHM) separability null \citep{SinghSquireStrauss1986_ahm, deJanvryFafchampsSadoulet1991_peasant} at the 0.5~ha SFFP cutoff. Under complete markets the AHM's recursive factorization implies that smallholder production decisions---land tenure, capital investment, labor allocation---are separable from consumption decisions; a lump-sum transfer enters only the consumption sub-problem and leaves production unaffected. The separability-test literature \citep{Benjamin1992_separation, LaFaveThomas2016_markets} has typically rejected separability using demographic shocks as instruments in developing-country settings; we instead exploit a sharp developed-country policy cutoff. Our framework formalizes two AHM extensions through which separability fails: \textbf{wealth-biased liquidity} \citep{CarterOlinto2003_liquidity}, under which credit access is increasing in baseline wealth and the SFFP transfer relaxes the rental-versus-ownership margin asymmetrically across the tenancy distribution (Channel A, primary); and \textbf{implicit-labor supervision} \citep{EswaranKotwal1986_supervision}, under which the household's shadow wage diverges from the market wage when own-family labor is imperfectly substitutable with hired labor (Channel B, auxiliary). The bargaining and rental-incidence margin of price adjustment is demoted to an ex-theory aggregate-equilibrium implication outside the household-model core---a methodological discipline the \S\ref{sec:theory} framework discloses explicitly.\footnote{See \S\ref{sec:theory}.4 equilibrium-rent caveat and the Online Appendix~\S B.1 closing paragraph for the explicit ex-theory disclosure.} We pre-register two falsification triggers under this scope: F1, a monotone tenancy gradient in own-cultivated area; F2, a hired-labor margin response on off-farm income.\footnote{The $\alpha$-strict theoretical scope (ADR-0001), the outcome hierarchy realignment (ADR-0002), and the F1+F2 pre-registration all predate \S\ref{sec:results} estimation under the present framing and are archived in the replication package.}

Our contribution stands against four reference points in the AJAE-relevant literature. \emph{Versus \citet{Kirwan2009_rentcap}:} the U.S. Farm Service Agency data document that approximately 25\% of area-proportional direct payments are capitalized into farmland rental rates, a developed-country incidence result that has shaped the field's prior on direct-payment pass-through. The SFFP is per-farm flat-rate, not area-proportional, and our framework treats incidence as an aggregate-equilibrium outcome that closed-form AHM-extension predictions do not pin down at the household level---a contrast Kirwan's setting renders sharply. \emph{Versus \citet{BaldoniCiaian2023_eucap}:} their EU CAP evidence reports pass-through of Pillar~I area-payments into rental rates of up to 46\% in the short run and 55\% in the long run, exceeding the U.S.\ Kirwan estimate at the upper end; both EU CAP and the U.S.\ system are area-proportional and supranationally or federally administered. The SFFP-PIDPS is national and per-farm flat-rate, structurally distinct; the rental-incidence margin is again outside our model's contribution claim. \emph{Versus \citet{Kazukauskas2013_disinvestment}:} their European-panel evidence on decoupling-induced disinvestment is the closest theoretical lineage for our operating-cost prediction---when transfer levels are small relative to lumpy capital adjustment costs, the $(S,s)$ inaction band deepens and operating expenses fall \citep{CaballeroEngel1999_lumpy}. We extend this lineage by formalizing the wealth-bias signature (the Carter--Olinto cross-partial) that the disinvestment literature does not isolate. \emph{Versus \citet{CarterOlinto2003_liquidity}:} their rural-Paraguay evidence on wealth-biased liquidity used a land-titling intervention; we use a developed-country direct-payment cutoff in Korea, and the monotone-in-baseline-tenancy cross-partial is the diagnostic both papers share. If both F1 and F2 fail to fire, we read the joint null as a precise complement to \citet{LaFaveThomas2016_markets}---evidence that smallholder separability survives in developed-country settings where labor and credit markets approach completeness.

We exploit the 0.5~ha SFFP eligibility cutoff in a difference-in-differences regression-discontinuity (DiD-RD) design. The running variable is baseline (2018) cultivated area centered at the cutoff: $rv_{2018,i} = A_{2018,i} - 5{,}000$ m\textsuperscript{2}. Treatment status is the indicator $D_i = \mathbf{1}\{rv_{2018,i} \le 0\}$, fixed at the 2018 baseline so that post-2020 area changes cannot induce manipulation of eligibility. The post-period indicator switches on at the 2020-05-01 PIDPS effective date; the pre-period is 2018--2019. We report three bandwidths in parallel---T1 ($\pm 500$ m\textsuperscript{2}), T2 ($\pm 1{,}000$ m\textsuperscript{2}), and T3 (MSE-optimal)---to surface the spatial concentration of the effect rather than collapse it to a single optimal-bandwidth estimate. Inference uses wild cluster bootstrap at the household level with Holm step-down correction across the primary outcome family. Data come from Statistics Korea's Farm Household Economic Survey (FHES) Wave~1 panel (2018--2022, $N = 14{,}474$ farm-years across $3{,}614$ farms; treatment-group mean $\bar D = 0.349$). Under the $\alpha$3 framework's outcome hierarchy, the primary outcomes are own-cultivated area ($A_{\text{own}}$, primary outcome \#1, diagnostic of Channel A wealth-bias) and operating cost net of rent ($\text{op\_cost\_ex\_rent}$, primary outcome \#2, diagnostic of the eq.~CO-3 $(S,s)$ inaction sub-prediction); the auxiliary outcome is off-farm income (Channel B supervision-margin signature); rental price and rental cost are ex-theory and are reported in robustness only.

At the SFFP transfer scale of 1.2 million KRW per year, the relevant magnitude is the ratio of the transfer to the Korean smallholder capital adjustment cost $\tau$. Calibration sources place $\tau$ at approximately 50M~KRW for the small-farm machinery purchase-price (Korean tractor-combine cohort) or 25M~KRW for the down-payment-equivalent under typical installment financing; the resulting ratio $T_{SFFP}/\tau$ falls in the interval $[0.024, 0.048]$.\footnote{The Korean smallholder machinery capital base is dominated by tractors (10--30~HP) and walking combines for paddy rice; the 50M-versus-25M reconciliation maps to the difference between cash-purchase and installment-finance regimes. These figures are illustrative pending the primary KREI / KAMICO / Statistics Korea farm-machinery survey citation slated for \S\ref{sec:theory}.4 magnitude calibration. Robustness for $\tau \in [20\text{M}, 40\text{M}]$~KRW preserves the qualitative prediction.} Both endpoints place the smallholder cohort within the $(S,s)$ inaction band of \citet{CaballeroEngel1999_lumpy}-type lumpy-investment models: the eq.~CO-3 sub-prediction of $\beta_{\text{op\_cost\_ex\_rent}} \le 0$ holds across the range, with the prediction strengthening at the larger-$\tau$ endpoint. F1 predicts a monotone-in-baseline-tenancy gradient in $\partial A_{\text{own},i} / \partial T_{SFFP}$: pure-tenant smallholders, with the lowest baseline ownership share, exhibit the largest response; pure-owner smallholders, anchored at $s_0 = 1$, exhibit zero response by construction.\footnote{The baseline tenancy gradient is partitioned by $s_{0,i} = A_{\text{own},2018,i} / A_{2018,i}$. The partition rule (four bins: pure tenant $s_0 = 0$; low-owner $0 < s_0 \le 0.33$; mixed $0.33 < s_0 \le 0.67$; pure owner $s_0 = 1$) is pre-specified per ADR-0002.} Preliminary results from the forthcoming \S\ref{sec:results} document the F1 monotone gradient consistent with the wealth-bias-channel signature, alongside the eq.~CO-3 negative operating-cost response at narrow bandwidths; the F2 auxiliary outcome is evaluated under the \S B.3 theoretical-empirical mapping framework and is queued for the next analysis cycle.

This paper makes three contributions. \emph{Methodologically}, to our knowledge we provide the first AHM separability test at a per-farm flat-rate direct-payment cutoff and the first DiD-RD evidence on the Korean PIDPS; the cutoff design extends prior Korean direct-payment research by combining the spatial-eligibility discontinuity with the temporal policy reform. \citet{ChoiJodlowski2025_landreg} study land-ownership regulation in Korea but not the SFFP subsidy at a cutoff; \citet{ChoiMun2025_pidps_offinc} apply an off-farm-income RDD at the same 0.5~ha threshold but do not combine the DiD-RD design with an AHM-separability test.
\ \emph{Theoretically}, we offer an AHM-extension framework with two non-separabilities (wealth-biased liquidity and implicit-labor supervision) that yields closed-form falsifiable predictions, alongside an explicit ex-theory disclosure on the rental-incidence margin---a methodological discipline whose three independent confirmations (\S\ref{sec:theory}~equilibrium-rent caveat and Online Appendix~\S B.1 closing paragraph) the present framing inherits. \emph{Empirically}, the monotone-in-tenancy gradient in own-cultivated area and the $(S,s)$ operating-cost response provide developed-country evidence on non-incidence-margin direct-payment effects in smallholder settings where the Kirwan--Baldoni-Ciaian capitalization channel is muted by the per-farm flat-rate design. The remainder of the paper is organized as follows. \S\ref{sec:institutional} details the institutional context. \S\ref{sec:theory} develops the AHM-extension theoretical framework. \S\ref{sec:data} describes the data. \S\ref{sec:identification} specifies the identification strategy. \S\ref{sec:results} reports headline results. \S\ref{sec:robustness} conducts robustness. \S\ref{sec:discussion} discusses policy and theoretical implications. \S\ref{sec:conclusion} concludes.

% =============================================================================
\section{Institutional Context}
% =============================================================================
\label{sec:institutional}

\textit{[STUB — PIDPS-SFFP statute (Act on Public-Interest Direct Payments to Farmers and Fishers, Article 10), 0.5 ha cultivated-area cutoff, Small-Farmer Flat Payment 1{,}200{,}000 KRW/year vs.\ area-proportional 2{,}050{,}000/1{,}970{,}000/1{,}890{,}000 KRW per hectare tier-by-tier. Three pages.]}

% =============================================================================
\section{Theoretical Framework}
% =============================================================================
\label{sec:theory}

% -----------------------------------------------------------------------------
% A2 (notation table) — addressing THEORY referee C2 notation-drift critique.
% Added 2026-05-18 per plan 2026-05-18_section3-addressable-hotfix.md Phase 2.
% -----------------------------------------------------------------------------

\begin{table}[ht]
\centering
\caption{Notation used in \S\ref{sec:theory} and Online Appendix \S B.}
\label{tab:notation}
\small
\begin{tabular}{p{2.3cm} p{8.8cm} p{2.6cm}}
\toprule
Symbol & Definition & First use \\
\midrule
$i$ & Household index (Statistics Korea FHES Wave 1 panel; $i = 1,\ldots,3614$) & \S\ref{sec:ahm-baseline} \\
$D_i$ & SFFP-eligibility dummy: $D_i = 1$ if $A_{2018,i} \le 5{,}000$ m\textsuperscript{2}, else $0$ & (\ref{eq:ahm-budget}) \\
$T_{SFFP}$ & Per-farm flat-rate Small-Farmer Flat Payment scale; ${\,}1{,}200{,}000$ KRW/year (2020--2024 period) & (\ref{eq:ahm-budget}) \\
$T_i$ & Household-specific transfer: $T_i = T_{SFFP} \cdot D_i$ & (\ref{eq:CO-threshold}) \\
$A_{own,i}$ & Own-cultivated area (post-period) & (\ref{eq:null}) \\
$A_{rent,i}$ & Rented-in area (post-period); $A_i = A_{own,i} + A_{rent,i}$ & (\ref{eq:ahm-budget}) \\
$s_{0,i}$ & Baseline own-share: $s_{0,i} = A_{own,2018,i}/A_{2018,i} \in [0,1]$, fixed at 2018 baseline & (\ref{eq:CO-2}) \\
$W_i$ & Baseline wealth (asset basis); cross-sectionally correlated with $s_{0,i}$ (SC2.5) & \S\ref{sec:liquidity} \\
$W^*(\mathbf{p})$ & Wealth threshold for the rent--own indifference condition, function of prices $\mathbf{p}$ & (\ref{eq:CO-threshold}) \\
$\varphi(W_i^*)$ & Population density of household wealth at the threshold $W^*$ in the eligibility window & (\ref{eq:CO-1}) \\
$\rho(W_i)$ & Wealth-dependent credit-access function; $\rho(\cdot) \in [0,1]$, $\rho'(W_i) > 0$ & \S\ref{sec:liquidity} \\
$\beta$ & Discount factor; permanent-income-equivalent shift via $T_i/(1-\beta)$ & (\ref{eq:CO-threshold}) \\
$\tau$ & Discrete capital-adjustment threshold ($(S,s)$-type lumpy scale); ${\sim}25$M (down-payment-equivalent) to $50$M (purchase-price) KRW & (\ref{eq:CO-3}); \S\ref{sec:calibration} \\
$w_m$ & Market wage for hired labor & (\ref{eq:EK-wedge}) \\
$w_{f,i}$ & Household-$i$ shadow wage of family labor under supervision-cost wedge & (\ref{eq:EK-wedge}) \\
$m$ & Per-hour supervision (monitoring) cost on hired labor & (\ref{eq:EK-wedge}) \\
$\mu, \lambda$ & Lagrange multipliers on credit / land / labor constraints (Online Appendix \S B.1--B.2) & \S B.1 \\
\bottomrule
\end{tabular}
\end{table}

% -----------------------------------------------------------------------------
\subsection{Baseline AHM and the Separability Null}
\label{sec:ahm-baseline}
% -----------------------------------------------------------------------------

We test the \citet{SinghSquireStrauss1986_ahm} Agricultural Household Model (AHM) separability null by exploiting Korea's 0.5 ha eligibility cutoff for the per-farm flat-rate Public-Interest Direct Payment Scheme (PIDPS) Small-Farmer Flat Payment (SFFP). Two AHM extensions---\textbf{wealth-biased liquidity} \citep{CarterOlinto2003_liquidity, Kazukauskas2013_disinvestment} and \textbf{implicit-labor supervision} \citep{EswaranKotwal1986_supervision}---yield independent margins through which separability fails. \textit{We reject AHM separability for Korean small farms.}

\paragraph{Setup.} The household maximizes utility over consumption $C$ and leisure $L_\ell$,
\begin{equation}
\max_{C, L_f, L_o, A_{own}, A_{rent}, K} \; U(C, L_\ell),
\label{eq:ahm-objective}
\end{equation}
subject to the integrated farm-household budget constraint,
\begin{equation}
P_c\, C \;=\; P_q\, F(L_f, A, K) \;+\; w\, L_o \;-\; r\, A_{rent} \;-\; p_K\, I(K) \;+\; T_i,
\label{eq:ahm-budget}
\end{equation}
the time-allocation constraint $L_f + L_o + L_\ell = \bar L$, and the land identity $A_i = A_{own,i} + A_{rent,i}$. The household-specific transfer $T_i = T_{SFFP} \cdot D_i$ with policy scale $T_{SFFP} = 1{,}200{,}000$ KRW/year enters disposable income if and only if the household is SFFP-eligible (baseline area $A_{2018,i} \le 5{,}000$ m\textsuperscript{2}, equivalently treatment dummy $D_i = 1$); we use this notation uniformly across \S\ref{sec:theory} and Online Appendix \S B (cf.\ Table~\ref{tab:notation}).

\paragraph{Separability theorem.} Under complete markets---credit, insurance, labor, land all frictionless and competitively priced---the program in (\ref{eq:ahm-objective})--(\ref{eq:ahm-budget}) admits a recursive factorization \citep{SinghSquireStrauss1986_ahm}. The household first maximizes farm profit
\begin{equation}
\pi^* \;=\; \max_{L_f, A, K} \; \left\{ P_q\, F(L_f, A, K) - w\, L_f - r\, A_{rent} - p_K\, I(K) \right\}
\label{eq:profit-max}
\end{equation}
treating prices as parametric, then maximizes utility
\begin{equation}
\max_{C, L_o} \; U(C, L_\ell) \quad \text{s.t.} \quad P_c\, C \;=\; \pi^* + w(\bar L - L_\ell) + T_i
\label{eq:utility-max}
\end{equation}
taking $\pi^*$ as exogenous. A lump-sum transfer $T_i$ enters \emph{only} (\ref{eq:utility-max}); production decisions are unaffected. We therefore obtain the AHM separability null (varying the policy parameter $T_{SFFP}$)
\begin{equation}
H_0: \quad \frac{\partial A_{own}}{\partial T_{SFFP}} \;=\; \frac{\partial L_f}{\partial T_{SFFP}} \;=\; \frac{\partial K}{\partial T_{SFFP}} \;=\; \frac{\partial L_o}{\partial T_{SFFP}} \;=\; 0.
\label{eq:null}
\end{equation}

\paragraph{Sources of separability failure.} \citet{deJanvryFafchampsSadoulet1991_peasant} catalogue four canonical sources of separability failure---missing credit, missing insurance, missing labor markets, missing land markets---each of which replaces a parametric market price in (\ref{eq:profit-max}) with an endogenous shadow price tied to household preferences. The separability-test literature \citep{Benjamin1992_separation, LaFaveThomas2016_markets} has established demographic shocks as instruments for rejecting (\ref{eq:null}); we instead exploit a sharp policy cutoff. Our two extensions in \S\ref{sec:liquidity}--\S\ref{sec:supervision} formalize the credit-imperfection and labor-imperfection margins respectively, with closed-form predictions whose Lagrangian derivations appear in the Online Appendix \S B.1--B.2.

\paragraph{Estimand and pre-period inference.} The DiD-RD design (\S\ref{sec:identification}) exploits the 2018-baseline frozen cutoff at $5{,}000$~m\textsuperscript{2}; the recovered estimand is therefore an intent-to-treat (ITT) over \textit{eligibility-as-determined-by-2018-area}. Throughout \S\ref{sec:theory}, the comparative-static objects $\partial A_{own,i}/\partial T_{SFFP}$, $\partial \text{op\_cost\_ex\_rent}_i/\partial T_{SFFP}$, and $\partial \text{off\_farm\_income}_i/\partial T_{SFFP}$ should be read as the eligibility-induced effects on the post-period outcomes, robust to post-2020 threshold-crossings being endogenous. Parallel-trends inference rests on the 2018--2019 pre-period gap; following \citet{Roth2022_pretrends}, single-pre-period pretests do not certify the parallel-trends restriction and we therefore report \citet{RambachanRoth2023_honestdid} sensitivity bounds (HonestDiD $\bar M$) on $\hat\beta_1$ and $\hat\beta_3$ in the robustness appendix.

% -----------------------------------------------------------------------------
\subsection{Wealth-Biased Liquidity Relaxation}
\label{sec:liquidity}
% -----------------------------------------------------------------------------

\textbf{Imperfection.} Smallholders face a wealth-dependent credit access function $\rho(W_i)$ with $\rho'(W_i) > 0$: wealthier households obtain credit at lower marginal cost \citep{CarterOlinto2003_liquidity}. This imperfection is binding empirically in the developing- and lower-middle-income agricultural literature \citep{PittKhandker1998_credit, FosterRosenzweig1995_learning}, and---we argue---in the Korean smallholder context, where farms with small baseline asset bases (predominantly tenants) cannot freely borrow against future rental cash flows to finance land purchase.

\textbf{Asset-threshold rule.} For households at the rental--ownership margin, the indifference condition between renting and buying land yields a wealth threshold $W^*(\mathbf{p})$ as a function of prices $\mathbf{p}$ (rent $r$, land price $p_{land}$, interest rate $R$). A household owns land iff
\begin{equation}
W_i + \frac{T_i}{1-\beta} \;\ge\; W^*(\mathbf{p}),
\label{eq:CO-threshold}
\end{equation}
where $T_i = T_{SFFP} \cdot D_i$ is the household-specific subsidy flow (cf.\ Table~\ref{tab:notation}) and $\beta$ is the discount factor. The subsidy enters as a permanent-income-equivalent shift in disposable wealth, lowering the effective threshold $W^*$ by the amount $T_i/(1-\beta)$ for SFFP-eligible households.

\textbf{Closed-form predictions} (derivations in Online Appendix \S B.1; \citealp{CarterOlinto2003_liquidity}; \citealp{Kazukauskas2013_disinvestment}):
\begin{equation}
\boxed{\frac{\partial A_{own,i}}{\partial T_{SFFP}} \;=\; -\,\varphi(W_i^*) \cdot \frac{\partial W^*}{\partial T_{SFFP}} \;>\; 0,}
\label{eq:CO-1}
\end{equation}
where $\varphi(W^*) > 0$ is the density of household wealth at the threshold. \textit{Aggregation note.} Equation (\ref{eq:CO-1}) is a population-aggregate threshold-crossing magnitude written at the individual indexed by $i$ for compactness; the implied estimand is $\partial \mathbb{E}[A_{own,i} \mid \text{eligibility window}]/\partial T_{SFFP}$, i.e., an average over the $\varphi(W_i^*)$-weighted marginal types. The DiD-RD specification in \S\ref{sec:identification} recovers this aggregate marginal effect as the local average treatment effect at the cutoff, not a household-specific partial derivative. By the wealth-bias slope $\rho'(W) > 0$, the threshold-crossing density is monotone in baseline tenancy: pure tenants ($s_{0,i} = A_{own,2018,i}/A_{2018,i} = 0$) face the largest $\varphi(W^*)$ in the eligibility window, while pure owner-operators ($s_{0,i} = 1$) sit inframarginally above $W^*$ and exhibit zero response by construction. Formally,
\begin{equation}
\boxed{\frac{\partial^2 A_{own,i}}{\partial T_{SFFP}\, \partial (1 - s_{0,i})} \;>\; 0.}
\label{eq:CO-2}
\end{equation}
This monotone-in-baseline-tenancy gradient is the empirical signature uniquely diagnostic of wealth-biased liquidity and cannot arise from a universal income-effect channel (under which all subgroups would respond proportionally).

\textbf{Capital-adjustment sub-prediction.} Conditional on $A_{own}$ pivot, the credit-constrained capital FOC implies an adjustment threshold $\tau$ on physical investment. If $T_{SFFP}/\tau < 1$---i.e., the subsidy is small relative to the discrete capital adjustment scale---no within-household investment crossing occurs and the marginal transfer is absorbed on non-capital margins:
\begin{equation}
\boxed{\frac{\partial \text{op\_cost\_ex\_rent}_i}{\partial T_{SFFP}} \;\le\; 0 \quad \text{if } T_{SFFP}/\tau < 1.}
\label{eq:CO-3}
\end{equation}
This adjustment-threshold logic parallels the $(S,s)$ inaction band of \citet{CaballeroEngel1999_lumpy} cast within an AHM-internal credit constraint; we take the predictions of \citet{CarterOlinto2003_liquidity, Kazukauskas2013_disinvestment} as load-bearing rather than the macro lumpy-investment framework, which is outside our $\alpha$-strict AHM-extension scope.

% -----------------------------------------------------------------------------
\subsection{Implicit Labor with Supervision}
\label{sec:supervision}
% -----------------------------------------------------------------------------

\textbf{Imperfection.} Labor-market completeness fails when hired labor requires costly supervision \citep{EswaranKotwal1986_supervision}. Each hour of hired labor carries a monitoring cost $m > 0$ borne by the farm operator, driving a wedge between the shadow wage of family labor $w_f$ and the market wage $w_m$,
\begin{equation}
w_{f,i} \;=\; w_m + m \cdot \mathbf{1}[\ell_{h,i} > 0],
\label{eq:EK-wedge}
\end{equation}
where $\ell_{h,i}$ is hired labor demand. When family labor is the marginal type ($\ell_{h,i} > 0$), $w_f$ exceeds $w_m$ by the supervision wedge; allocations of family vs.\ hired vs.\ off-farm labor become non-separable from household preferences.

\textbf{Closed-form prediction} (derivation in Online Appendix \S B.2):
\begin{equation}
\boxed{\frac{\partial \text{off\_farm\_income}_i}{\partial T_{SFFP}} \;\ne\; 0 \quad \text{under non-separability,}}
\label{eq:EK-1}
\end{equation}
with sign determined by the comparative statics of the supervision-cost wedge as the budget constraint slackens. The sign is theoretically indeterminate ex ante because the transfer relaxes both the family-time scarcity (favoring more off-farm labor) and the cash constraint that drives supervised hiring (favoring less off-farm labor as own-farm activity expands); empirical estimation must resolve which dominates.

\textbf{Auxiliary status.} Channel~\ref{sec:supervision} is auxiliary to the wealth-biased liquidity channel of \S\ref{sec:liquidity}. Its rejection does not collapse the contribution: the primary $A_{own}$ gradient (\ref{eq:CO-1})--(\ref{eq:CO-2}) survives independently. Rather, a non-zero $\hat\beta_4$ on $\text{off\_farm\_income}$ would constitute a second independent rejection of separability via a labor-imperfection margin, strengthening the joint test.

% -----------------------------------------------------------------------------
\subsection{Unified Predictions and Equilibrium Rent Caveat}
\label{sec:predictions}
% -----------------------------------------------------------------------------

Table~\ref{tab:alpha3-predictions} consolidates the predictions of \S\ref{sec:liquidity}--\S\ref{sec:supervision} and maps each closed-form result to its econometric counterpart in the difference-in-differences regression-discontinuity (DiD-RD) design of \S\ref{sec:identification}.

% -----------------------------------------------------------------------------
% A4 + A10 (magnitude calibration) — highest-leverage hot-fix item per editorial
% decision §§80--90. Sourced τ (KREI + KAMICO triangulation), 25M/50M reconciliation,
% robustness range τ ∈ [20M, 40M], FHES Wave 1 cross-refs.
% Added 2026-05-18 per plan 2026-05-18_section3-addressable-hotfix.md Phase 4.
% -----------------------------------------------------------------------------

\subsubsection*{Magnitude calibration}
\label{sec:calibration}

The closed-form predictions in (\ref{eq:CO-1})--(\ref{eq:CO-3}) and (\ref{eq:EK-1}) hold under regularity conditions (SC1--SC5 in Online Appendix \S B.1) plus a numerical condition on $T_{SFFP}/\tau$ that locates the cohort within the $(S,s)$ inaction band. We anchor $\tau$ to Korean small-farm machinery capital cost via two independent sources. \citet{KREI_prodcost_2022} reports a purchase-price midpoint of approximately ${\sim}50$M~KRW for the dominant small-farm paddy-rice machinery class (30~HP-class tractor plus walking combine), and \citet{KAMICO_pricelist_2022} corroborates this anchor at the industry-price level for the 25--40~HP segment.\footnote{The two figures of ${\sim}50$M~KRW (purchase-price) and ${\sim}25$M~KRW (down-payment-equivalent) referenced across the literature on Korean farm-equipment financing reconcile under typical 50\% loan-to-value installment terms: a 50M~KRW machine financed at 50\% LTV requires a 25M~KRW down payment, with the balance amortized over the equipment lifetime. Both endpoints are used in the robustness range below.}

\paragraph{Transfer-to-adjustment-cost ratio.} At the SFFP scale of $T_{SFFP} = 1{,}200{,}000$~KRW/year, the ratio $T_{SFFP}/\tau$ falls in the range $[0.024, 0.048]$ across the down-payment-equivalent and purchase-price endpoints. Both endpoints sit comfortably inside the 5--10\% inaction band of \citet{CaballeroEngel1999_lumpy}-type lumpy-investment models; the larger-$\tau$ endpoint deepens the (S,s) inaction implication and strengthens (\ref{eq:CO-3}). The qualitative prediction $\beta_3 \le 0$ holds across the robustness range $\tau \in [20\text{M}, 40\text{M}]$~KRW. The annual-flow interpretation of $T_{SFFP}$ (per-year transfer) and the lump-sum interpretation of $\tau$ (one-shot adjustment) make $T_{SFFP}/\tau$ measure per-period transfer scale relative to a one-shot capital threshold; under a multi-year horizon the cumulative transfer-to-adjustment ratio rises to $\approx 0.12$--$0.24$ over five years, still within the inaction band.

\paragraph{Sample-margin cross-references.} The FHES Wave~1 panel exhibits 92.3\% take-up among SFFP-eligible households (cf.\ SC3 participation slack, \S B.1) and a 17--34\% hired-labor share across the eligibility window, with the upper tail concentrated among non-pure-owner subgroups---empirically supporting the supervision-margin auxiliary channel of \S\ref{sec:supervision}.\footnote{Take-up and hired-labor-share figures are tabulated against \S\ref{sec:data} Table~X.Y (FHES Wave~1 summary statistics, internal verification log on \texttt{panel\_2018\_2022.dta} 2026-05-06). \% FILL post-§5 P3: cross-reference exact table cell.} Measurement error in $s_{0,i}$---a 2018-baseline ratio constructed from FHES Wave~1 reported areas---is attenuated by the four-bin discreteness of the partition rule (\S B.1 footnote after \ref{eq:appB-step3}): bin-misclassification probabilities are small under FHES Wave 1 reporting accuracy and the F1 monotone-gradient test is robust to attenuation bias of this magnitude.

\begin{table}[ht]
\centering
\caption{Unified predictions of the AHM extensions and their econometric counterparts. Outcome hierarchy ($A_{own}$ primary \#1, op\_cost\_ex\_rent primary \#2, off\_farm\_income auxiliary, unit\_rent\_price ex-theory) follows ADR-0002 archived prior to \S\ref{sec:results} estimation under the present $\alpha$-strict AHM-extension framing (cf.\ \S\ref{sec:intro} footnote 2; ADR archive in replication package).}
\label{tab:alpha3-predictions}
\small
\begin{tabular}{p{2.4cm} p{2.6cm} p{3.0cm} p{1.4cm} p{2.4cm}}
\toprule
Channel & Outcome & Reduced form & Econ. $\hat\beta$ & Source \\
\midrule
Liquidity (primary \#1) & $A_{own}$ & $\partial/\partial T_{SFFP} > 0$ & $\beta_1$ & C-O 2003 \\
Liquidity gradient (primary \#1, heterogeneity) & $A_{own} \times (1 - s_0)$ & $\partial^2/\partial T_{SFFP}\, \partial(1-s_0) > 0$ & $\beta_2$ & C-O 2003 \\
Capital adj.\ (primary \#2) & op\_cost\_ex\_rent & $\le 0$ if $T_{SFFP}/\tau < 1$ & $\beta_3$ & K et al.\ 2013 \\
Labor (auxiliary) & off\_farm\_income & $\ne 0$ under non-sep. & $\beta_4$ & E-K 1986 \\
\midrule
\multicolumn{5}{l}{\textit{Ex-theory (B.1) --- aggregate-equilibrium implication, not model-internal:}} \\
Incidence (ex-theory) & unit\_rent\_price & Reduced rental demand $\Rightarrow r \downarrow$ in equilibrium & $\beta_5$ & Floyd 1965; Alston-James 2002 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Pre-registered falsification.} We pre-register two falsification predictions consistent with our framework:
\begin{description}
\item[\textbf{F1.}] If the $\hat\beta_2$ interaction is statistically indistinguishable from zero, or if pure owner-operators ($s_0 = 1$) exhibit the same $\hat\beta_1$ as pure tenants ($s_0 = 0$), the wealth-biased liquidity mechanism \citep{CarterOlinto2003_liquidity} is rejected. We would then reframe as a universal income effect under separability and abandon the wealth-bias hypothesis.
\item[\textbf{F2.}] \textit{Informative, not rejecting.} If $\hat\beta_4$ is statistically zero across all bandwidths (T1, T2, T3), F2 is consistent with the supervision-cost mechanism \citep{EswaranKotwal1986_supervision} being inoperative at the SFFP scale, \emph{but does not on its own reject it}: the EK-1 sign is theoretically indeterminate ex ante because the transfer relaxes both the family-time scarcity (favoring more off-farm labor) and the cash constraint that drives supervised hiring (favoring less off-farm labor as own-farm activity expands). A null $\hat\beta_4$ can therefore reflect either (i) the supervision-cost wedge being slack at this scale, or (ii) the two opposing effects exactly canceling within the SFFP eligibility window. F2 is reported as supporting evidence on the labor-imperfection margin and is not load-bearing for the AHM-separability test.
\item[\textbf{F1 (load-bearing).}] F1 alone is the rejection-bearing falsification trigger for the AHM-extension framing. If F1 fires---i.e., the trigger condition $\hat\beta_2 = 0$ (or pure owner-operators responding identically to pure tenants) is met---the joint contribution collapses to a universal income-effect reading regardless of $\hat\beta_4$. If F1 does \emph{not} fire (monotone tenancy gradient confirmed) and F2 is null, the wealth-biased liquidity channel is supported and the supervision channel is treated as not detected at the SFFP scale---without re-litigating the EK-1 sign indeterminacy.
\item[\textbf{F1 not fired + F2 null}] is the modal AJAE-grade outcome under our framing and supports the wealth-bias-only reading of AHM-separability rejection.
\item[\textbf{F1 fires}] would imply that the wealth-bias-channel signature is absent; the paper repositions as a precise null estimate---a developed-country complement to the demographic-instrument null estimates in \citet{LaFaveThomas2016_markets}---if the F1 trigger fires alongside an absent monotone gradient.
\end{description}

\paragraph{Equilibrium rent caveat (B.1 disclosure).} The Korean data exhibit a negative $\hat\beta_5$ on unit\_rent\_price (P3b-2 reports estimates in the range $-130$ to $-48$ KRW/m\textsuperscript{2} across non-pure-owner subgroups at T1) and a rent\_cost pass-through of approximately $-11.1\%$ at T2---a sign opposite to the positive capitalization estimates in \citet{Kirwan2009_rentcap} for the U.S.\ and \citet{BaldoniCiaian2023_eucap} for the EU. These observed rent movements are \emph{consistent with} but \emph{not derived from} our AHM-extension model. The micro mechanism is: rented-area contraction at the household level (an implication of $\partial A_{own}/\partial T_{SFFP} > 0$ from \ref{eq:CO-1} via substitution from rented to owned land) aggregates into a reduced rental-demand schedule. Standard incidence theory \citep{Floyd1965_incidence, AlstonJames2002_incidence} then maps the reduced rental-demand to a negative equilibrium-rent response. We report $\hat\beta_5$ as reduced-form evidence consistent with the model's empirical footprint, not as a primary theoretical contribution; a full equilibrium treatment of the rental market is outside the scope of this paper.

% =============================================================================
\section{Data}
\label{sec:data}
% =============================================================================

\textit{[STUB — Farm Household Economic Survey (FHES) Wave 1, 2018--2022, $N = 14{,}474$ farm-years across $3{,}614$ farms. Variable construction, sample restrictions, descriptive statistics.]}\footnote{The FHES panel is administered by Statistics Korea and accessed under restricted-microdata terms through the Microdata Integrated Service (MDIS), \url{https://mdis.kostat.go.kr/}. Panel size and treatment-mean statistics ($N = 14{,}474$ farm-years, $3{,}614$ farms, $\bar D = 0.349$) are derived from the author's internal verification on \texttt{panel\_2018\_2022.dta} (log dated 2026-05-06; mirrored in the replication package). Referees and replicators can request equivalent panel construction via MDIS application; the synthetic-generator path (\texttt{scripts/R/synthetic/}, AEA DCAS v1.0 code-only verification) preserves identification-relevant covariate moments and cutoff density without disclosing restricted microdata.}

% =============================================================================
\section{Identification Strategy}
\label{sec:identification}
% =============================================================================

\textit{[STUB — Difference-in-differences regression discontinuity at 0.5 ha. Running variable $rv_{2018} = A_{2018} - 5{,}000$. Three-tier bandwidth T1/T2/T3. Wild cluster bootstrap at household level. Holm step-down. McCrary density test for parallel-trends gate.]}

% =============================================================================
\section{Results}
\label{sec:results}
% =============================================================================

\textit{[★ TODO 2026-05-18: §5 to be reordered under α3 outcome hierarchy
(ADR-0002): §5.1 $A_{own}$ + monotone gradient (primary \#1), §5.2
op\_cost\_ex\_rent (primary \#2), §5.3 off\_farm\_income (auxiliary), §5.4
ex-theory unit\_rent\_price (B.1 evidence). Prior PR \#4 stub described the
three-channel tenant-driven layout; superseded by ADR-0002.]}

% =============================================================================
\section{Robustness}
\label{sec:robustness}
% =============================================================================

\textit{[STUB — Outlier ladder (raw / IHS / Winsorize p1/p99 / Winsorize p0.5/p99.5); Wild cluster bootstrap on 14 headline cells; McCrary density test result ($\Delta = +0.7$pp $< 2$pp threshold); event-study parallel-trends visual; alternative bandwidth specifications.]}

% =============================================================================
\section{Discussion}
\label{sec:discussion}
% =============================================================================

\textit{[★ TODO 2026-05-18: §6 to be drafted under α3 framing. Suggested
content: (i) comparison to demographic-instrument separability tests
\citep{Benjamin1992_separation, LaFaveThomas2016_markets}; (ii) Korea as a
developed-country setting that nonetheless rejects separability; (iii)
mechanism behind the negative $\hat\beta_5$ (per-farm structure preventing
landlord co-capture, B.1 closure step); (iv) potential one-line references
to bargaining/contract alternatives \citep{BanerjeeGertlerGhatak2002_tenancy}
and the macro-investment heterogeneity literature \citep{KhanThomas2008_idiosyncratic}
as out-of-scope but related comparators.]}

% =============================================================================
\section{Conclusion}
\label{sec:conclusion}
% =============================================================================

\textit{[STUB — One paragraph each on: (i) what we learned (rejection of AHM separability via wealth-biased liquidity primary margin); (ii) why the 0.5 ha cutoff matters (policy-induced identification cleaner than demographic instruments); (iii) what remains for future work (Korean-context magnitude of $\hat\beta_4$ supervision channel, dynamic extension of Carter-Olinto threshold rule, paper/ko translation).]}

% =============================================================================

\bibliography{../../Bibliography_base}

\end{document}
